Fontawesome

### 2022-07-19 Shiny/Test/Fontawesome.Rmd
Icon idea.
Icon ideas.

```{r}
# Creating df
df <- fontawesome::fa_metadata()
# Version check
df$version
# Example search
df$icon_names_full |> str_view_all("skull", match = TRUE)
```

>>>>

```{r}
# Creating df
df <- fontawesome::fa_metadata()
# Version check
df$version
# Example search
df$icon_names_full |> str_view_all("hands-helping", match = TRUE)
```

### Ideas

#### Checked

- fas fa-seedling
- fas fa-donate
- fas fa-hand-holding-usd
- fas fa-hands-helping

#### Not yet checked

#### Not available
